Variation in Primary Care Prescribing in Wales due to COVID-19

### 2022-04-27 writing/paper.Rmd
Tidying

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data"))
names(data_files) <-
  str_remove_all(list.files("../data/prescribing_data"), ".rds")
# 
# gp_extract <- 
#   map_dfr(.x = data_files[1:11],
#           .f = ~(read_rds(.x)),
#           .id = "drug")

# Functions

@@

@@

@@

```{r, table-2}
tibble(regional_unit = unique(differences$regional_unit)) %>% 
  left_join(read_rds("../data/gp_agesex_qof_combined.rds") %>% 
              mutate(npat = N,
                     N = NULL,
                     regional_unit = as.character(practiceid)) %>% 
              ungroup() %>% 
              janitor::clean_names() %>%  
              filter(year == 2020)) %>% 
  select(npat, ngp, dispensing, wimd2019:flu) %>% 
  mutate(across(p_male:flu, ~.x*100)) %>% 
  tibble() %>% 
  psych::describe(fast = TRUE) %>% 
  kable(digits = 2, caption = "Summary of prescribing data and GP practice characteristics")
```

```{r}
plan(cluster)
pres_2019 <- 
  data_files[c(1:10)] %>% 
  furrr::future_map(read_rds) %>% 
  furrr::future_map(monthlyPrescribing) %>% 
  furrr::future_map_dfr(as_tibble, .id = "drug") %>% 
  filter(year(datename) == 2019)
plan(sequential)

pres_2019 %>% 
  right_join(differences %>% 
               group_by(regional_unit, drug) %>% 
               count() %>% 
               select(-n), by = c("drug", "regional_unit")) %>% 
  filter(drug != "warfarin_ddd") %>% 
  bind_rows(read_rds(data_files[12]) %>% 
              mutate(drug = "warfarin_ddd",
                datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
              rename(regional_unit = practice_id,
                     n = quantity) %>% 
              filter(year(datename) == 2019)) %>% 
  group_by(drug) %>% 
  summarise(mean = mean(n, na.rm = TRUE),
            sd = sd(n, na.rm = TRUE),
            min = min(n, na.rm = TRUE),
            max = max(n, na.rm = TRUE)) %>% 
  left_join(differences %>% 
              dplyr::group_by(drug) %>% 
              dplyr::count() %>% 
              mutate(n = n/8), by = "drug") %>% 
  select(drug, n, everything()) %>% 
  kable(digits = 2)
```

@@

differences_quantiles %>%
  dplyr::mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  dplyr::mutate(drug = case_when(drug == "all_drugs" ~ "All",
                          drug == "ace" ~ "ACEi",
                          drug == "cortico" ~ "Inhaled cortico",
                          drug == "hcq" ~ "HCQ",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "oral_contra" ~ "Oral contra",
                          drug == "paracet" ~ "Paracet",
                          drug == "sal" ~ "Salbutamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vit D",
                          drug == "warfarin" ~ "Warfarin",
                          drug == "warfarin_ddd" ~"Warfarin"),
         drug = relevel(as_factor(drug), ref = "All"),
         line_type = if_else(Percentile == "50%", "Median", "Decile")) %>%
  ggplot(aes(x = datename, col = drug, 
             group = Percentile)) +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  geom_line(aes(y = prop, lty = line_type)) +
  geom_hline(aes(yintercept = 0), alpha = .5) +
  facet_wrap(~drug, scales = "free") + 
  guides(size = "legend", colour = "none") + 
  theme(text = element_text(size = 10),
        legend.position = c(1, 0),
        legend.justification = c(1, 0)) +
  scale_linetype_manual(values = c(2,1), name = " ") +
  xlab("Month") +
  ylab("Percentage difference from forecast dispensing")

@@

```{r, fig-2-single-fcts, eval=TRUE, fig.cap="Estimated percentage change [95% CI] from forecast dispensing. Grey line marks the level of forecast dispensing. Pink shading covers duration of Wales’ “stay at home” order. Please note the different y-axis scales across the plots. ACEi = ACE inhibitors, HCQ = Hydroxycholoroquine."}
plan(cluster)
nat_data <- # Data for all regional units combined
  data_files %>% 
  furrr::future_map_dfr(read_rds, .id = "drug") %>% 
  filter(drug != "warfarin_ddd") %>% 
  dplyr::group_by(drug, datename) %>% 
  dplyr::summarise(n = sum(quantity, na.rm = TRUE), .groups = "drop") %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% # Calling drug regional_unit to save rewriting all the code
  as_tsibble(index = "datename", key = "regional_unit") %>% 
  fill_gaps()

@@

lockdown_fcsts <- 
  nat_data %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  filter(!regional_unit %in% best_mape_over_50$regional_unit) %>% 
  fableModels() %>%
  generate(h = 8, times = 1000) %>%
  as_tibble() %>% 
  filter(!datename %in% 
           yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug", "2020 Sept", "2020 Oct"))) %>% 
  group_by(.model, regional_unit, .rep) %>% 
  dplyr::summarise(.sim = sum(.sim)) %>%
  # Store as a distribution
  dplyr::summarise(total = distributional::dist_sample(list(.sim))) %>% 
  mutate(mean = mean(total),
         lb_95 = stats::quantile(total, .025),
         lb_80 = stats::quantile(total, .1),
         med = median(total),
         ub_80 = stats::quantile(total, .9),
         ub_95 = stats::quantile(total, .975),
         sd = distributional::variance(total)^.5,
         total = NULL)

three_month_fcsts <- 
  nat_data %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  filter(!regional_unit %in% best_mape_over_50$regional_unit) %>% 
  fableModels() %>%
  generate(h = 8, times = 1000) %>%
  as_tibble() %>% 
  filter(datename > yearmonth("2020 Feb") &
                       datename < yearmonth("2020 Jun")) %>% 
  group_by(.model, regional_unit, .rep) %>% 
  dplyr::summarise(.sim = sum(.sim)) %>%
  # Store as a distribution
  dplyr::summarise(total = distributional::dist_sample(list(.sim))) %>% 
  mutate(mean = mean(total),
         lb_95 = stats::quantile(total, .025),
         lb_80 = stats::quantile(total, .1),
         med = median(total),
         ub_80 = stats::quantile(total, .9),
         ub_95 = stats::quantile(total, .975),
         sd = distributional::variance(total)^.5,
         total = NULL)

@@

#### Joint table ####
lockdown_diffs %>% 
  left_join(monthly_diffs, by = "regional_unit") %>% 
  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>%
  kable_styling(font_size = 8) %>% 
  add_header_above(header = c(" " = 1,
                              "Mean percentage change [95% CI]" = 9)) %>%
  landscape()

@@

```{r, gls-functions, echo=FALSE}
drugs <- unique(differences$drug) # Remove? Should be in setup

## Assumption checking? ##

@@

```{r, gls-analysis-save, results="asis", warning=FALSE, message=FALSE, eval = FALSE}
#### gls-analysis-save ####
drugs <- unique(differences$drug)

best_models <- list()
best_bs_models <- list()

```{r, gls-anova-summary-tab}
best_bs_models <- read_rds("../data/gls/best_bs_models.rds")

#### ANOVA Table ####
best_bs_models %>% 
  map(~anova(., tol = 1e-10)) %>% 
  map(~as_tibble(x = ., rownames = "Variable")) %>% 
  map(as.matrix) %>% 
  map(as_tibble) %>% 
  bind_rows(.id= "drug") %>% 
  mutate(across(`Chi-Square`:P, as.numeric)) %>% 
  select(-c(`Chi-Square`, d.f.)) %>% 
  filter(!str_detect(Variable, "Nonlinear") &
           !str_detect(Variable, "TOTAL") &
           !str_detect(Variable,"All Interactions"),
         !str_detect(Variable, c("f" %R% OPEN_PAREN %R% "A,B"))) %>%
  pivot_wider(names_from = drug, values_from = P) %>% 
  mutate(across(ace:warfarin, ~printnum(., zero = FALSE)),
         Variable = str_remove_all(Variable, OPEN_PAREN %R% "Factor" %R% PLUS %R% 
                                 "Higher Order Factors" %R% CLOSE_PAREN)) %>% 
  select(Variable, all_drugs, everything()) %>% 
  kable(booktabs = TRUE, linesep = "",
        caption = paste("Wald test p-values")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 
  landscape()
```

@@

```{r, gp-2020-percentiles, include=FALSE}
gp_2020_percentiles <- 
  data.frame(
    percentile = c(5, 25, 50, 75, 95),
    # wimd2019 = percentiles(gp_2020, wimd2019),
    ngp = percentiles(gp_2020, ngp),
    gp_load = percentiles(gp_2020, gp_load),
    PC1 = percentiles(gp_2020, PC1),
    PC2 = percentiles(gp_2020, PC2),
    PC3 = percentiles(gp_2020, PC3),
    PC4 = percentiles(gp_2020, PC4))

@@

* Figures represent predicted changes to dispensing based on GLS models
* When considering the effect of a specific predictor over time, all other predictors will be set to the median value for continuous predictors and the mode for categorical predictors.
*

### Month

```{r gls-month-fig, fig.cap="Dispensing by health board", eval=FALSE}
dd <- NULL
gls_month_fig <- list()
for(i in drugs){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  gls_month_fig[[i]] <- 
    Predict(best_bs_models[[i]], Month, 
            hboard = "BC", dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
            gp_load = 1329.486, 
            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
            conf.int = .95)

  options(datadist = NULL)
}

gls_month_fig %>% 
  map_dfr(as_tibble, .id = "drug") %>% 
  mutate(drug = as.factor(drug),
           drug = relevel(drug, ref = "all_drugs")) %>%
  ggplot(aes(x = Month, y = yhat)) +
  geom_line() +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0) +
  facet_wrap(~drug, scales = "free_y")

* This is broadly a repeat of what is seen in Figure 2 and what is described in the text referring to that section, therefore will not be repeated here.

### Health board

```{r gls-hb-fig-panel, fig.cap="Dispensing by health board"}
dd <- NULL
gls_hb_fig <- list()
for(i in drugs_hb){
  dd <- datadist(glsData(i))
  options(datadist = "dd")
  gls_hb_fig[[i]] <- 
    Predict(best_bs_models[[i]], Month, hboard,
            dispensing = FALSE, wimd2019 = "Med", ngp = 5, 
            gp_load = 1329.486, 
            PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
            PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
            conf.int = .95)

  options(datadist = NULL)
}

gls_hb_fig %>% 
  map_dfr(as_tibble, .id = "drug") %>% 
  dplyr::mutate(Month = factor(x = Month, levels = 3:8, 
                           labels = month.abb[3:8]),
                drug = case_when(drug == "all_drugs" ~ "All",
                          drug == "ace" ~ "ACEi",
                          drug == "cortico" ~ "Inhaled \ncorticosteriods",
                          drug == "hcq" ~ "HCQ",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "oral_contra" ~ "Oral \ncontraceptives",
                          drug == "paracet" ~ "Paracetamol",
                          drug == "sal" ~ "Salbutamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vitamin D",
                          drug == "warfarin" ~ "Warfarin",
                          drug == "warfarin_ddd" ~"Warfarin")) %>% 
  ggplot(aes(x = Month, y = yhat, col = as.factor(hboard), group = hboard)) +
  geom_line(alpha = 0, position = position_dodge(.7)) +
  geom_point(position = position_dodge(.7), size = .5) +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = .5, 
                position = position_dodge(.7)) +
  ggthemes::theme_few() +
  guides(col = guide_legend(ncol = 2)) +
  theme(legend.position = c(.8,.1),
        legend.title = element_text(size = 10, face = "bold", hjust = .5),
        legend.text = element_text(size = 10)) +
  scale_colour_viridis_d("Health board") +
  facet_wrap(~drug, scales = "free_y")

ggsave(filename = "Draft 5/Figures/health-board.png", device = "png", height = 14, width = 25, units = "cm")

* Seven of the eleven groups of medicines were dispensed differently across health boards.
*

@@

                         list(Month = 3:8, hboard = "BC", wimd2019 = "Med", 
                              ngp = 5, gp_load = 1329,

@@

disp_contrasts %>% 
  arrange(drug) %>% 
  kable

@@

                       list(Month = 3:8, hboard = "BC", wimd2019 = "Low", 
                            ngp = 5, gp_load = 1329,

@@

                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                            ngp = 5, gp_load = 1329,

@@

wimd_contrasts %>% 
  arrange(drug) %>% 
  kable

@@

```{r, ngp-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
ngp_contrasts <- 
  list(
    oral_contra = contrast(best_bs_models$oral_contra, 
                           list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                                ngp = 3, gp_load = 1329,
                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                                dispensing = FALSE),
                           list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                                ngp = 8, gp_load = 1329,
                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                                dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    sal = contrast(best_bs_models$sal, 
                   list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                        ngp = 3, gp_load = 1329,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE),
                   list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                        ngp = 8, gp_load = 1329,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()) %>% 
  bind_rows(.id = "drug")

@@

ngp_contrasts %>% 
  arrange(drug) %>% 
  kable

@@

```{r, gpld-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
gpld_contrasts <- 
  list(
    oral_contra = contrast(best_bs_models$oral_contra, 
                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                        ngp = 8, gp_load = 1098,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE),
                       list(Month = 3:8, hboard = "BC", wimd2019 = "High", 
                        ngp = 8, gp_load = 1710,
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()) %>% 
  bind_rows(.id = "drug")

@@

gpld_contrasts %>% 
  arrange(drug) %>% 
  kable

@@

```{r, summary-plot}
# names(drugs) <- c("ACE inhibitors", "Inhaled corticosteriods", "
#                   Hydroxychloroquine", "Non-steroidal anti-inflamatory drugs",
#                   "Oral contraceptives", "Paracetamol", "Salbutamol", )

>>>>

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data"))
names(data_files) <-
  str_remove_all(list.files("../data/prescribing_data"), ".rds")

#### Functions ####

@@

#### Assumption checking ####
glsAssump <- function(model, data){
  data$resid <- r <- resid(model); data$fitted <- fitted(model)
  y1 <- ylab("Residuals")
  p1 <- ggplot(data, aes(x = fitted, y = resid)) + geom_point(alpha = .1) + y1
  p2 <- ggplot(data, aes(x = Month, y = resid)) + y1 + 
    stat_summary(fun.data = "mean_sdl", geom = "smooth")
  p3 <- ggplot(data, aes(sample = resid)) + stat_qq(alpha = .1) + 
    geom_abline(intercept = mean(r), slope = sd(r)) + y1
  p4 <- textGrob(drugs[i])

  gridExtra::grid.arrange(p1, p2, 
                          p3, p4, ncol = 2)
}

@@

drugs <- unique(differences$drug)
drugs <- factor(drugs)
drugs <- relevel(drugs, ref = "all_drugs")
```

@@

### 2019 dispensing summary

```{r, table-2a}
tibble(regional_unit = unique(differences$regional_unit)) %>% 
  left_join(read_rds("../data/gp_agesex_qof_combined.rds") %>% 
              mutate(npat = N,
                     N = NULL,
                     regional_unit = as.character(practiceid)) %>% 
              ungroup() %>% 
              janitor::clean_names() %>%  
              filter(year == 2020),
            by = "regional_unit") %>% 
  select(npat, ngp, dispensing, wimd2019:flu) %>% 
  mutate(across(p_male:flu, ~.x*100),
         dispensing = if_else(dispensing == "Yes", 1, 0)) %>% 
  tibble() %>% 
  psych::describe(fast = TRUE) %>% 
  kable(digits = 2, caption = "Summary of prescribing data and GP practice characteristics")
```

### 2020 GP practice summary

```{r, table-2b}
plan(cluster)
pres_2019 <- 
  data_files[c(1:10)] %>% 
  furrr::future_map(read_rds) %>% 
  furrr::future_map(monthlyPrescribing) %>% 
  furrr::future_map_dfr(as_tibble, .id = "drug") %>% 
  filter(year(datename) == 2019) %>% 
  mutate(drug = relevel(as_factor(drug), ref = "quant_all_drugs"),
         drug = str_remove_all(drug, "ddd_"),
         drug = str_remove_all(drug, "quant_"),
         drug = str_remove_all(drug, "_ddd"))
plan(sequential)

pres_2019 %>% 
  left_join(differences %>% 
               group_by(regional_unit, drug) %>% 
               count() %>% 
               select(-n), by = c("drug", "regional_unit")) %>% 
  filter(drug != "warfarin_ddd") %>% 
  bind_rows(read_rds(data_files["warfarin_ddd"]) %>% 
              mutate(drug = "warfarin_ddd",
                     datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
              rename(regional_unit = practice_id,
                     n = quantity) %>% 
              filter(year(datename) == 2019)) %>% 
  group_by(drug) %>% 
  summarise(mean = mean(n, na.rm = TRUE),
            sd = sd(n, na.rm = TRUE),
            min = min(n, na.rm = TRUE),
            max = max(n, na.rm = TRUE)) %>% 
  mutate(drug = relevel(as_factor(drug), ref = "all_drugs")) %>% 
  select(drug, everything()) %>% 
  arrange(drug) %>% 
  kable(digits = 2)
```

@@

differences_quantiles %>%
  dplyr::mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  dplyr::mutate(drug = case_when(drug == "all_drugs" ~ "All dispensing",
                          drug == "ace" ~ "ACEi",
                          drug == "cortico" ~ "Inhaled cortico",
                          drug == "hcq" ~ "HCQ",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "oral_contra" ~ "Oral contra",
                          drug == "paracet" ~ "Paracet",
                          drug == "sal" ~ "Salbutamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vit D",
                          drug == "warfarin" ~ "Warfarin",
                          drug == "warfarin_ddd" ~"Warfarin"),
         drug = relevel(as_factor(drug), ref = "All dispensing"),
         line_type = if_else(Percentile == "50%", "Median", "Decile")) %>%
  ggplot(aes(x = datename, col = drug, 
             group = Percentile)) +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  geom_line(aes(y = prop, lty = line_type)) +
  geom_hline(aes(yintercept = 0), alpha = .5) +
  facet_wrap(~drug, scales = "free") + 
  guides(size = "legend", colour = "none") + 
  theme(text = element_text(size = 10),
        legend.position = c(1, 0),
        legend.justification = c(1, 0)) +
  scale_linetype_manual(values = c(2,1), name = " ") +
  xlab("Month") +
  ylab("Percentage difference from forecast dispensing")

@@

```{r, fig-2-single-fcts, eval=TRUE, fig.cap="Estimated percentage change [95% CI] from forecast dispensing. Grey line marks the level of forecast dispensing. Pink shading covers duration of Wales’ “stay at home” order. Please note the different y-axis scales across the plots. ACEi = ACE inhibitors, HCQ = Hydroxycholoroquine.", cache=TRUE}
plan(cluster)
nat_data <- # Data for all regional units combined
  data_files %>% 
  furrr::future_map_dfr(read_rds, .id = "drug") %>% 
  filter(drug != "warfarin_ddd") %>% 
  dplyr::group_by(drug, datename) %>% 
  dplyr::summarise(n = sum(quantity, na.rm = TRUE), .groups = "drop") %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% # Calling drug regional_unit to save rewriting all the code
  as_tsibble(index = "datename", key = "regional_unit") %>% 
  fill_gaps()

@@

lockdown_fcsts <- 
  nat_data %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  filter(!regional_unit %in% best_mape_over_50$regional_unit) %>% 
  fableModels() %>%
  generate(h = 8, times = 1000) %>%
  as_tibble() %>% 
  filter(!datename %in% 
           yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug", "2020 Sept", "2020 Oct"))) %>% 
  group_by(.model, regional_unit, .rep) %>% 
  dplyr::summarise(.sim = sum(.sim), 
                   .groups = "drop_last") %>%
  # Store as a distribution
  dplyr::summarise(total = distributional::dist_sample(list(.sim)), 
                   .groups = "drop_last") %>% 
  mutate(mean = mean(total),
         lb_95 = stats::quantile(total, .025),
         lb_80 = stats::quantile(total, .1),
         med = median(total),
         ub_80 = stats::quantile(total, .9),
         ub_95 = stats::quantile(total, .975),
         sd = distributional::variance(total)^.5,
         total = NULL)

three_month_fcsts <- 
  nat_data %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  filter(!regional_unit %in% best_mape_over_50$regional_unit) %>% 
  fableModels() %>%
  generate(h = 8, times = 1000) %>%
  as_tibble() %>% 
  filter(datename > yearmonth("2020 Feb") &
                       datename < yearmonth("2020 Jun")) %>% 
  group_by(.model, regional_unit, .rep) %>% 
  dplyr::summarise(.sim = sum(.sim),
                   .groups = "drop_last") %>%
  # Store as a distribution
  dplyr::summarise(total = distributional::dist_sample(list(.sim)),
                   .groups = "drop_last") %>% 
  mutate(mean = mean(total),
         lb_95 = stats::quantile(total, .025),
         lb_80 = stats::quantile(total, .1),
         med = median(total),
         ub_80 = stats::quantile(total, .9),
         ub_95 = stats::quantile(total, .975),
         sd = distributional::variance(total)^.5,
         total = NULL)

@@

#### Joint table ####
lockdown_diffs %>% 
  left_join(monthly_diffs, by = "regional_unit") %>% 
  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>%
  kable_styling(font_size = 10) %>% 
  add_header_above(header = c(" " = 1,
                              "Mean percentage change [95% CI]" = 9)) %>%
  landscape()

@@

```{r, gls-analysis-save, results="asis", warning=FALSE, message=FALSE, eval = FALSE}
#### gls-analysis-save ####
best_models <- list()
best_bs_models <- list()

```{r, gls-analysis-read}
#### gls-analysis-read ####
best_models <- read_rds("../data/gls/best_models.rds")
best_bs_models <- read_rds("../data/gls/best_bs_models.rds")
```

```{r, gls-functions, echo=FALSE}
#### Assumption checking ####
dd <- NULL
for(i in 1:length(best_bs_models)){
  gls_data <- glsData(drugs[i])
  dd <- datadist(gls_data)
  options(datadist = "dd")
  glsAssump(best_bs_models[[i]], gls_data)
  rm(dd)
  options(datadist = NULL)
}

@@

```{r, gls-anova-summary-tab}
#### ANOVA Table ####
best_bs_models %>% 
  map(~anova(., tol = 1e-10)) %>% 
  map(~as_tibble(x = ., rownames = "Variable")) %>% 
  map(as.matrix) %>% 
  map(as_tibble) %>% 
  bind_rows(.id= "drug") %>% 
  mutate(across(`Chi-Square`:P, as.numeric)) %>% 
  select(-c(`Chi-Square`, d.f.)) %>% 
  filter(!str_detect(Variable, "Nonlinear") &
           !str_detect(Variable, "TOTAL") &
           !str_detect(Variable,"All Interactions"),
         !str_detect(Variable, c("f" %R% OPEN_PAREN %R% "A,B"))) %>%
  pivot_wider(names_from = drug, values_from = P) %>% 
  mutate(across(ace:warfarin, ~printnum(., zero = FALSE)),
         Variable = str_remove_all(Variable, OPEN_PAREN %R% "Factor" %R% PLUS %R% 
                                 "Higher Order Factors" %R% CLOSE_PAREN)) %>% 
  select(Variable, all_drugs, everything()) %>% 
  kable(booktabs = TRUE, linesep = "",
        caption = paste("Wald test p-values")) %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "repeat_header")) %>% 
  landscape()
```

@@

```{r, gp-2020-percentiles, include=FALSE}
(gp_2020_percentiles <- 
   data.frame(
     percentile = c(5, 25, 50, 75, 95),
     ngp = percentiles(gp_2020, ngp),
     gp_load = percentiles(gp_2020, gp_load),
     PC1 = percentiles(gp_2020, PC1),
     PC2 = percentiles(gp_2020, PC2),
     PC3 = percentiles(gp_2020, PC3),
     PC4 = percentiles(gp_2020, PC4)))

@@

@@

                         list(Month = 3:8, wimd2019 = "Med", 
                              ngp = median(gp_2020$ngp), 
                              gp_load = median(gp_2020$gp_load),

@@

disp_contrasts %>% 
  arrange(drug) %>% 
  mutate(across(where(is.numeric), printnum),
         contrast = paste0(Contrast, "[", Lower, ",", Upper, "]"),
         Month = factor(x = Month, levels = 3:8,
                           labels = month.abb[3:8])) %>%
  pivot_wider(id_cols = drug, values_from = contrast, names_from = Month) %>%
  kable(align = "r") %>%
  kable_styling() %>%
  landscape()
```

@@

                   list(Month = 3:8, wimd2019 = "Low", 
                        ngp = median(gp_2020$ngp), 
                        gp_load = median(gp_2020$gp_load),

@@

                   list(Month = 3:8, wimd2019 = "High", 
                        ngp = median(gp_2020$ngp), 
                        gp_load = median(gp_2020$gp_load),

@@

wimd_contrasts %>% 
  arrange(drug) %>% 
  mutate(across(where(is.numeric), printnum),
         contrast = paste0(Contrast, "[", Lower, ",", Upper, "]"),
         Month = factor(x = Month, levels = 3:8,
                           labels = month.abb[3:8])) %>%
  pivot_wider(id_cols = drug, values_from = contrast, names_from = Month) %>%
  kable(align = "r") %>%
  kable_styling() %>%
  landscape()

@@

```{r, ngp-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
ngp_contrasts <- 
  list(
    oral_contra = contrast(best_bs_models$oral_contra, 
                           list(Month = 3:8, wimd2019 = "Med", 
                                ngp = 3, 
                                gp_load = median(gp_2020$gp_load),
                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                                dispensing = FALSE),
                           list(Month = 3:8, wimd2019 = "Med", 
                                ngp = 8, 
                                gp_load = median(gp_2020$gp_load),
                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                                dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame(),
    sal = contrast(best_bs_models$sal, 
                   list(Month = 3:8, wimd2019 = "Med", 
                        ngp = 3, 
                        gp_load = median(gp_2020$gp_load),
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE),
                   list(Month = 3:8, wimd2019 = "Med", 
                        ngp = 8, 
                        gp_load = median(gp_2020$gp_load),
                        PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                        PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                        dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()) %>% 
  bind_rows(.id = "drug")

@@

ngp_contrasts %>% 
  arrange(drug) %>% 
  mutate(across(where(is.numeric), printnum),
         contrast = paste0(Contrast, "[", Lower, ",", Upper, "]"),
         Month = factor(x = Month, levels = 3:8,
                           labels = month.abb[3:8])) %>%
  pivot_wider(id_cols = drug, values_from = contrast, names_from = Month) %>%
  kable(align = "r") %>%
  kable_styling() %>%
  landscape()

@@

```{r, gpld-contrast-fig, fig.cap="NGP contrasts and 95% confidence limits from GLS models."}
gpld_contrasts <- 
  list(
    oral_contra = contrast(best_bs_models$oral_contra, 
                           list(Month = 3:8, wimd2019 = "Med",
                                ngp = median(gp_2020$ngp), 
                                gp_load = 1098,
                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                                dispensing = FALSE),
                           list(Month = 3:8, wimd2019 = "Med", 
                                ngp = median(gp_2020$ngp), 
                                gp_load = 1710,
                                PC1 = median(gp_2020$PC1), PC2 = median(gp_2020$PC2), 
                                PC3 = median(gp_2020$PC3), PC4 = median(gp_2020$PC4),
                                dispensing = FALSE)) %>% 
      .[c("Month", "Contrast", "Lower", "Upper")] %>% 
      as.data.frame()) %>% 
  bind_rows(.id = "drug")

@@

gpld_contrasts %>% 
  arrange(drug) %>% 
  mutate(across(where(is.numeric), printnum),
         contrast = paste0(Contrast, "[", Lower, ",", Upper, "]"),
         Month = factor(x = Month, levels = 3:8,
                           labels = month.abb[3:8])) %>%
  pivot_wider(id_cols = drug, values_from = contrast, names_from = Month) %>%
  kable(align = "r") %>%
  kable_styling() %>%
  landscape()

@@

```{r, summary-plot}
contrasts <- 
  bind_rows(disp_contrasts, wimd_contrasts, ngp_contrasts, gpld_contrasts,
            .id = "effect") %>% 
  mutate(Month = factor(x = Month, levels = 3:8, 
                           labels = month.abb[3:8]),
         effect = case_when(effect == 1 ~ "Dispensing - Non-dispensing",
                            effect == 2 ~ "High - Low WIMD",
                            effect == 3 ~ "8 GPs - 3 GPs",
                            effect == 4 ~ "1710 per GP - 1098 per GP"),
         drug = case_when(drug == "all_drugs" ~ "All dispensing",
                          drug == "ace" ~ "ACEi",
                          drug == "cortico" ~ "Inhaled \ncorticosteriods",
                          drug == "hcq" ~ "HCQ",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "oral_contra" ~ "Oral \ncontraceptives",
                          drug == "paracet" ~ "Paracetamol",
                          drug == "sal" ~ "Salbutamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vitamin D",
                          drug == "warfarin" ~ "Warfarin",
                          drug == "warfarin_ddd" ~"Warfarin"),
         drug = factor(drug),
         effect = factor(effect,
                         levels = c("Dispensing - Non-dispensing", 
                                    "High - Low WIMD",
                                    "8 GPs - 3 GPs", 
                                    "1710 per GP - 1098 per GP")))
